### 2025-01-27 our_article/MCM_article/article_file.tex
论文修改

          $\gamma$ & Activity of decomposer\\
          $A_i,B_i$ & Effect of the predator-prey relationship on population $i$ (specified coefficient).\\
          $D_i,E_i$ & Effect of shortage of food on population $i$ (specified coefficient)\\
          $N,P,K$ & Chemical elements\\

@@

      \begin{equation}
        \begin{aligned}
          \frac{\mathrm{d}W_{crp}}{\mathrm{d}t}&=r_{crp}W_{crp}\left( 1-\frac{W_{crp}+\beta _{w\rightarrow c}W_{wd}}{\mathscr{K} _{crp}} \right) -\frac{A_{crp}W_{crp}W_{ins}}{1+B_{crp}W_{crp}}\\
          \frac{\mathrm{d}W_{wd}}{\mathrm{d}t}&=r_{wd}W_{wd}\left( 1-\frac{W_{wd}+\beta _{c\rightarrow w}W_{crp}}{\mathscr{K} _{wd}} \right) -\frac{A_{wd}W_{wd}W_{ins}}{1+B_{wd}W_{wd}}\\
          \frac{\mathrm{d}W_{ins}}{\mathrm{d}t}&=r_{ins}W_{ins}\left[ 1-\frac{D_{ins}W_{ins}}{1+E_{ins}\left( 0.6W_{crp}+0.4W_{wd} \right)} \right] -\frac{A_{ins}W_{ins}W_{bd}}{1+B_{ins}W_{ins}}\\
          \frac{\mathrm{d}W_{bd}}{\mathrm{d}t} &= r_{bd}W_{bd} \left[ 1 - \frac{D_{bd}W_{bd}}{1 + E_{bd}(0.2W_{ins} + 0.2W_{wd} + 0.6W_{crp})} \right]\\
        \end{aligned} 
      \end{equation}

@@

      The first three equations consider the effect of predation through the term(e.g. the first one) 
      $\frac{A_{crp} W_{crp} W_{ins}}{1 + B_{crp} W_{crp}}.$

      The last two equations(e.g. the third one) include the term 
        $\frac{D_{ins} W_{ins}}{1 + E_{ins} \left( 0.6 W_{crp} + 0.4 W_{wd} \right)}$,
      which represents biomass reduction due to food scarcity. 
      In the denominator, one factor is weighted according to the predation ratio: the less food available, 
      the more predators there are, resulting in a slower growth rate of the predator population.
    \subsection{Model II: CAGED Model}
      CAGED Model represents Conprehensive Agro-Ecosystem Dynamics Model, and it is the core model of the hole article.
      Model I is quite simple and aims to construct a basic short-term model. 
      Considering the impact of long-term environmental factors, 
      in order to better simulate the long-term evolutionary behavior of the ecosystem model, 
      we will progressively introduce the effects of simplified agricultural cycles, 
      seasonality, soil fertility, pollination, random factors and multiple digestion delays on the system dynamics model. 
      Furthermore, we will consider the impact of chemical use, 
      specifically the application of herbicides and pesticides, on the system, 
      building upon this natural agricultural ecosystem model.
      \subsubsection{Agricultural Cycle}
        According to rice production in Indonesia(\figurename~\ref{fig:PlantModePlus}), 
        rice production in Southeast Asia follows a three-crop-per-year pattern. 
        We assume that February, June, and October are the overlapping periods of two agricultural cycles 
        (from the last post-harvest period to the new planting period).
        \begin{figure}[H]
          \centering
          \includegraphics[width=0.7\linewidth]{images/PlantModePlus.png}
          \caption{Overlapping Periods of Two Agricultural Cycles}
          \label{fig:PlantModePlus}
        \end{figure}
        During the overlapping period, the rice population re-enters the food web in the form of seeds after harvesting, 
        starting a new agricultural cycle. The mature rice straw, as an agricultural byproduct, 
        remains in the ecosystem after harvesting, and after being treated by methods such as burning or returning to the field, 
        the rice biomass is decomposed and ingested by decomposers and insects, ultimately decreasing to zero.

@@

        \begin{equation}
          \frac{\mathrm{d}W_{stw}}{\mathrm{d}t} = \frac{A_{stw} W_{stw} W_{ins}}{1 + B_{stw} W_{stw}} \quad (t \neq n)
        \end{equation}
        \begin{equation}
          W_{stw}|_{t=n} = W_{stw}|_{t=n-1} + 0.09 W_{crp}|_{t=n-1},\\
          n = 52k, 52k+17, 52k+34, \quad (k \geqslant 0, \, n \geqslant 1)
        \end{equation}
        The difference equation for insect biomass is modified as follows:
        \begin{equation}
          \frac{\mathrm{d}W_{ins}}{\mathrm{d}t} = r_{ins} W_{ins} \left[ 1 - \frac{D_{ins} W_{ins}}{1 + E_{ins} \left( 0.6 W_{crp} + 0.4 W_{wd} + W_{stw} \right)} \right] - \frac{A_{ins} W_{ins} W_{bd}}{1 + B_{ins} W_{ins}}
        \end{equation}

@@

        Regarding the CO$_2$ concentration term, 
        since the agricultural ecosystem is an open system and, 
        in our context, can be considered to be surrounded by a vast and complex forest ecosystem, 
        the impact of respiration from the components of the agricultural ecosystem on the atmospheric CO$_2$ concentration can be neglected. 
        Thus, the CO$_2$ concentration is approximated as a constant, \( C_{CO_2} \). 
        Based on this, we introduce the soil fertility factor \( \mu_{fri} = f(C_{isi}) \). 
        Soil fertility has a complex and profound effect on parameters such as the growth rate of population biomass, 
        competition coefficients, and the maximum carrying capacity of the environment. 
        An important consideration here is the effect of \( \mu \) on the environmental maximum biomass carrying capacity, 
        as shown below:

        \[
        \frac{\mathrm{d}W_{i}}{\mathrm{d}t} = r_{i} W_{i} \left( 1 - \frac{W_{i} + \beta_{j \rightarrow i} W_{j}}{\mathscr{K}_{i} \cdot \mu_{fri}} \right) - \frac{A_{i} W_{i} W_{ins}}{1 + B_{i} W_{i}}
        \]

@@

        \[
        C_{isi}(t) = \alpha_{isi} e^{-\frac{(t - T_{mc})^2}{\sigma_{isi}}}
        \]

        where \( T \) represents the time at which the concentration of inorganic salts in rice or weeds is at its maximum during a cycle; the remaining two parameters correspond to the model constants for rice or weeds, and are determined by fertilizer concentration (from both chemical fertilizers and straw), decomposer activity, and the plant’s growth stage.

        Again, for the sake of model simplification, we assume \( \mu_{fri} = \xi_{i} C_{isi} \).
      \subsubsection{Random Factors}
        Considering the influence of random factors in nature, we introduce Gaussian white noise \(\sigma_i\) for each population.

@@

        Our generation method is as follows:
        \begin{itemize}
            \item Generate two distinct random functions \(U_1(t)\) and \(U_2(t)\) within the interval \([0, 1]\);
            \item Take \(\eta(t) = -\sqrt{-2 \ln U_1(t)} \cdot \cos(2\pi U_2(t))\), which gives \(\eta(t)\) as the Gaussian white noise function.
        \end{itemize}
        The noise corresponding to different species in the equations is shown in \figurename~\ref{fig:GussianNoise}.
        \begin{figure}[H]
          \centering
          \includegraphics[width=0.8\linewidth]{images/GussianNoise.png}
          \caption{Gussian Noises of Each Population}
          \label{fig:GussianNoise}
        \end{figure}
      \subsubsection{Chemical Use}
        For herbicides, considering that the application times of herbicides during rice cultivation are primarily before sowing, 
        at the seedling stage, and at the tillering stage, we assume that herbicides are applied three times during an agricultural cycle, 
        with the application occurring at weeks 0, 3, and 8. The herbicide concentration is proportional to the current weed biomass. 
        Since the application frequency is relatively low, we can ignore the specific negative effects of herbicides on rice 
        (any minor negative effects can be covered by the random process described in random factors).

@@

        \begin{equation}
        C_{hc}|_{t=m} = C_{hc}|_{t=m-1} + \alpha_{uh} W_{wd}|_{t=m},
        \end{equation}
        \begin{equation}
        \frac{dW_{wd}}{dt} = r_{wd}W_{wd} \left( 1 - \frac{W_{wd} + \beta_{c \rightarrow w} W_{crp}}{\mathscr{K}_{wd}} \right) - \frac{A_{wd} W_{wd} W_{ins}}{1 + \beta_{wd} W_{wd}} - \frac{A_{hc} W_{wd} C_{hc}}{1 + B_{hc} W_{wd}},
        \end{equation}
        \begin{equation}
        \frac{dC_{hc}}{dt} = - \alpha_{dh} C_{hc}.
        \end{equation}

@@

        \begin{equation}
          \begin{split}
            \frac{dW_{ins}}{dt} = r_{ins} W_{ins} &\left( 1 - \frac{D_{ins} W_{ins}}{1 + E_{ins} \left[ (0.6 - \lambda_{pc}) W_{crp} + (0.4 + \lambda_{prc}) W_{wd} \right]} \right) \\
            &-\frac{A_{ins} W_{ins} W_{bd}}{1 + \beta_{ins} W_{ins}} - \frac{A_{pc} W_{ins} C_{pc}}{1 + B_{pc} W_{ins}},
          \end{split}
      \end{equation}

@@

  \section{Appication of the Models}
    The process of model establishment has been thoroughly presented in the previous subsection. 
    In this subsection, we will discuss the application of the model.
    \subsection{Selection of Parameters}
      After reviewing the literature and aligning the parameters with their real-world significance, 
      we have determined a series of parameters. Due to the large number of parameters, 
      we will only present the table for the main ones:
      \begin{table}[H]
        \centering
        \caption{Parameters}
        \begin{tabular}{cc}
          \toprule
          \rowcolor{customcolor!40} % 设置背景颜色
          Symbols & Description\\
          \midrule
          $123$ & 123\\
          \bottomrule
        \end{tabular}
        \label{tab:Parameters}
      \end{table}
      All of the following models will apply these parameters.
      \subsection{Scenarios Statement}
        \begin{table}[H]
          \centering
          \caption{Notations}
          \begin{tabular}{lccccccc}
            \toprule
            \rowcolor{customcolor!40} % 设置背景颜色
            conditions & Description\\
            \midrule
            Agro-Activities & Y & Y & Y & Y & Y & Y \\

            \bottomrule
          \end{tabular}
          \label{tab:Notations}
        \end{table}
      \subsection{Scenario 1: No Agricultural Activities}
        This scenario will serve as a control group for familiarizing with the model. 
        We consider a situation without chemicals, sowing, or harvesting, 
        but with the migration of other species (since the migration of other species is an inevitable result of ecosystem maturation). 
        In this situation, we obtained the following population dynamics curve.
        \begin{figure}[H]
        \end{figure}
        From the figure, we can observe that under Scenario 1, the ecosystem develops normally, 
        but rice cannot survive in the long term, meaning the system cannot evolve into an agricultural ecosystem. 
        This indicates that the competitive ability of rice against weeds and its resistance to pests are relatively weak, 
        preventing it from sustainably existing in the ecosystem without human intervention. 
        This result is consistent with real-world observations and serves as the first validation of the model's accuracy.
      \subsection{Scenario 2: Chemicals or Green Agriculture Solutions Used}
        In the discussion of Scenario 2, we consider a realistic situation. 
        A farmer has just cleared a forest to plant rice. 
        Initially, he uses chemicals such as herbicides and pesticides to suppress weeds and pests as the ecosystem gradually develops. 
        When the ecosystem matures to a certain extent, some species that had migrated from the forest ecosystem return, 
        enriching the food web of the farmland ecosystem. After further development, the ecosystem becomes relatively stable, 
        and the farmer stops using herbicides and pesticides, 
        instead turning to a green agriculture solution by introducing ducks and bats into the system.
        Specifically:
        \begin{itemize}
          \item The physiology of ducks prevents them from eating rice, but they can consume weeds and pests.
          \item Ducks are introduced two weeks after each sowing season and are harvested simultaneously with rice at the end of the season.
          \item Bats are introduced all at once and serve as both pollinators and insect predators.
        \end{itemize}
        When the system evolved mature, the final food web of traditional farming mode and green farming mode are shown in 
        Figure \ref{fig:food_web_chem} and Figure \ref{fig:food_web_green} respectively.
        \begin{figure}[H]
          \begin{minipage}[b]{0.45\linewidth}
            \centering
            \includegraphics[height=6cm, keepaspectratio]{images/food_web_chem.pdf}
            \caption{Traditional Mode}
            \label{fig:food_web_chem}
          \end{minipage}
          \hspace{0.05\linewidth}
          \begin{minipage}[b]{0.45\linewidth}
              \centering
              \includegraphics[height=6cm, keepaspectratio]{images/food_web.pdf} % 替换为你的第二张图片路径
              \caption{Green Mode}
              \label{fig:food_web_green}
          \end{minipage}
        \end{figure}
        We will focus on comparing the succession of the ecosystem in the scenarios where humans use chemicals 
        (conventional scenario) and where humans use green agriculture solutions (target scenario). 
        In both cases, the ecosystem is unstable during the initial phase, 
        so we only show the dynamic behavior of the ecosystem after it reaches a stable state.

>>>>

          $\gamma_{i \rightarrow j}$ & Percentage of i in j's total food consumption\\
          $A_{i\rightarrow j},B_{i\rightarrow j}$ & Effect of $i\rightarrow j$ pred-prey relationship on population $i$ \\
          $D_i,E_i$ & Effect of shortage of food on population $i$ \\

@@

      \begin{equation}
        \begin{aligned}
          \frac{\mathrm{d}W_{crp}}{\mathrm{d}t}&=r_{crp}W_{crp}\left( 1-\frac{W_{crp}+\beta _{w\rightarrow c}W_{wd}}{\mathscr{K} _{crp}} \right) -\sum_{{j=pred}}{\frac{A_{crp\rightarrow j}W_{crp}W_{j}}{1+B_{crp\rightarrow j}W_{crp}}}\\
          \frac{\mathrm{d}W_{wd}}{\mathrm{d}t}&=r_{wd}W_{wd}\left( 1-\frac{W_{wd}+\beta _{c\rightarrow w}W_{crp}}{\mathscr{K} _{wd}} \right) -\sum_{{j=pred}}{\frac{A_{wd\rightarrow j}W_{wd}W_{j}}{1+B_{wd\rightarrow j}W_{wd}}}\\
          \frac{\mathrm{d}W_{ins}}{\mathrm{d}t}&=r_{ins}W_{ins}\left[ 1-\frac{D_{ins}W_{ins}}{1+E_{ins}\left( 0.6W_{crp}+0.4W_{wd} \right)} \right] -\frac{A_{ins\rightarrow bd}W_{ins}W_{bd}}{1+B_{ins\rightarrow bd}W_{ins}}\\
          \frac{\mathrm{d}W_{bd}}{\mathrm{d}t} &= r_{bd}W_{bd} \left[ 1 - \frac{D_{bd}W_{bd}}{1 + E_{bd}(0.2W_{ins} + 0.2W_{wd} + 0.6W_{crp})} \right]\\
        \end{aligned} 
      \end{equation}

@@

      For population $i$, the first three equations consider the effect of predation($i\rightarrow j$, which means $j$ hunts $i$) through the term

      \begin{equation}
      \sum_{j=pred}{\frac{A_{i\rightarrow j}W_{i}W_{j}}{1+B_{i\rightarrow j}W_{i}}}
      \end{equation}

      In the term above, we can see that when the biomass of predators(here, namely, insects and birds) increases, 
      the rate of increasing of certain prey will recude due to the hunting effects.

      The last two equations(e.g. the third one) include the term

        \begin{equation}
          \frac{D_{i} W_{i}}{1 + E_{i} \sum_{j=food}{\gamma_{j\rightarrow i} W_{j}}},
        \end{equation}

          which represents biomass reduction due to food scarcity. 
      In the denominator, one factor is weighted according to the predation ratio: the less food available, 
      the more predators there are, resulting in a slower growth rate of the predator population.
    \subsection{Model II: CAGED Model}
      CAGED Model represents Conprehensive Agro-Ecosystem Dynamics Model, and it is the core model of the hole article.
      Model I is quite simple and aims to construct a basic short-term model. 
      Considering the impact of long-term environmental factors, 
      in order to better simulate the long-term evolutionary behavior of the ecosystem model, 
      we will progressively introduce the effects of simplified agricultural cycles, 
      seasonality, soil fertility, pollination, random factors and multiple digestion delays on the system dynamics model. 
      Furthermore, we will consider the impact of chemical use, 
      specifically the application of herbicides and pesticides, on the system, 
      building upon this natural agricultural ecosystem model.
      \subsubsection{Agricultural Cycle}
        According to rice production in Indonesia(\figurename~\ref{fig:PlantModePlus}), 
        rice production in Southeast Asia follows a three-crop-per-year pattern. 
        We assume that February, June, and October are the overlapping periods of two agricultural cycles 
        (from the last post-harvest period to the new planting period).
        \begin{figure}[H]
          \centering
          \includegraphics[width=0.7\linewidth]{images/PlantModePlus.png}
          \caption{Overlapping Periods of Two Agricultural Cycles}
          \label{fig:PlantModePlus}
        \end{figure}
        During the overlapping period, the rice population re-enters the food web in the form of seeds after harvesting, 
        starting a new agricultural cycle. The mature rice straw, as an agricultural byproduct, 
        remains in the ecosystem after harvesting, and after being treated by methods such as burning or returning to the field, 
        the rice biomass is decomposed and ingested by decomposers and insects, ultimately decreasing to zero.

@@

        \begin{equation}
          \frac{\mathrm{d}W_{stw}}{\mathrm{d}t} = \frac{A_{stw\rightarrow ins} W_{stw} W_{ins}}{1 + B_{stw\rightarrow ins} W_{stw}} \quad (t \neq n)
        \end{equation}

        \begin{equation}
          W_{stw}|_{t=n} = W_{stw}|_{t=n-1} + 0.09 W_{crp}|_{t=n-1},
        \end{equation}

        \begin{equation}
          n = 52k, 52k+17, 52k+34, \quad (k \geqslant 0, \, n \geqslant 1, k,n\ are\ positive\ integers)
        \end{equation}
        The difference equation for insect biomass is modified as follows:
        \begin{equation}
          \frac{\mathrm{d}W_{ins}}{\mathrm{d}t} = r_{ins} W_{ins} \left[ 1 - \frac{D_{ins} W_{ins}}{1 + E_{ins} \left( 0.6 W_{crp} + 0.4 W_{wd} + W_{stw} \right)} \right] - \frac{A_{ins\rightarrow bd} W_{ins} W_{bd}}{1 + B_{ins\rightarrow bd} W_{ins}}
        \end{equation}

@@

        Regarding the CO$_2$ concentration term, 
        since the agricultural ecosystem is an open system and, 
        in our context, can be considered to be surrounded by a vast and complex forest ecosystem, 
        the impact of respiration from the components of the agricultural ecosystem on the atmospheric CO$_2$ concentration can be neglected. 
        Thus, the CO$_2$ concentration is approximated as a constant, \( C_{CO_2} \). 
        Based on this, we introduce the soil fertility factor \( \mu_{Fr_i} = f(C_{Is_i}) \). 
        Soil fertility has a complex and profound effect on parameters such as the growth rate of population biomass, 
        competition coefficients, and the maximum carrying capacity of the environment. 
        An important consideration here is the effect of \( \mu \) on the environmental maximum biomass carrying capacity, 
        as shown below:

        \[
        \frac{\mathrm{d}W_{i}}{\mathrm{d}t} = r_{i} W_{i} \left( 1 - \frac{W_{i} + \beta_{j \rightarrow i} W_{j}}{\mathscr{K}_{i} \cdot \mu_{Fr_i}} \right) - \sum_{j=pred}{\frac{A_{i\rightarrow j} W_{i} W_{j}}{1 + B_{i\rightarrow j} W_{i}}}
        \]

@@

        \[
        C_{Is_i}(t) = \alpha_{Is_i} e^{-\frac{(t - T_{mc})^2}{\sigma_{Is_i}}}
        \]

        where \( T \) represents the time at which the concentration of inorganic salts in rice or weeds is at its maximum during a cycle; the remaining two parameters correspond to the model constants for rice or weeds, 
        and are determined by fertilizer concentration (from both chemical fertilizers and straw), decomposer activity, and the plant's growth stage.

        Again, for the sake of model simplification, we assume \( \mu_{Fr_i} = \xi_{i} C_{Is_i} \).
      \subsubsection{Random Factors}
        Considering the influence of random factors in nature, we introduce Gaussian white noise \(\sigma_i\) for each population.

@@

        Our generation method is as follows:
        \begin{itemize}
            \item Generate two distinct random functions \(U_1(t)\) and \(U_2(t)\) within the interval \([0, 1]\);
            \item Take \(\eta(t) = -\sqrt{-2 \ln U_1(t)} \cdot \cos(2\pi U_2(t))\), which gives \(\eta(t)\) as the Gaussian white noise function.
        \end{itemize}
        The noise corresponding to different species in the equations is shown in \figurename~\ref{fig:GussianNoise}.
        \begin{figure}[H]
          \centering
          \includegraphics[width=0.5\linewidth]{images/GussianNoise.png}
          \caption{Gussian Noises of Each Population}
          \label{fig:GussianNoise}
        \end{figure}
      \subsubsection{Chemical Use}
        For herbicides, considering that the application times of herbicides during rice cultivation are primarily before sowing, 
        at the seedling stage, and at the tillering stage, we assume that herbicides are applied three times during an agricultural cycle, 
        with the application occurring at weeks 0, 3, and 8. The herbicide concentration is proportional to the current weed biomass. 
        Since the application frequency is relatively low, we can ignore the specific negative effects of herbicides on rice 
        (any minor negative effects can be covered by the random process described in random factors).

@@

        \begin{equation}
        C_{hc}|_{t=m} = C_{hc}|_{t=m-1} + \alpha_{uh} W_{wd}|_{t=m},
        \end{equation}
        \begin{equation}
        \frac{dW_{wd}}{dt} = r_{wd}W_{wd} \left( 1 - \frac{W_{wd} + \beta_{c \rightarrow w} W_{crp}}{\mathscr{K}_{wd}} \right) - \sum_{j=pred}{\frac{A_{wd\rightarrow j} W_{wd} W_{j}}{1 + B_{wd\rightarrow j} W_{wd}}} - \frac{A_{hc} W_{wd} C_{hc}}{1 + B_{hc} W_{wd}},
        \end{equation}
        \begin{equation}
        \frac{dC_{hc}}{dt} = - \alpha_{dh} C_{hc}.
        \end{equation}

@@

        \begin{equation}
          \begin{split}
            \frac{dW_{ins}}{dt} = r_{ins} W_{ins} &\left( 1 - \frac{D_{ins} W_{ins}}{1 + E_{ins} \left[ (0.6 - \lambda_{pc}) W_{crp} + (0.4 + \lambda_{prc}) W_{wd} \right]} \right) \\
            &-\frac{A_{ins\rightarrow bd} W_{ins} W_{bd}}{1 + B_{ins\rightarrow bd} W_{ins}} - \frac{A_{pc} W_{ins} C_{pc}}{1 + B_{pc} W_{ins}},
          \end{split}
      \end{equation}

@@

  \section{Appication of the Models}
    The process of model establishment has been thoroughly presented in the previous subsection. 
    In this subsection, we will discuss the application of the model.
    \subsection{Selection of Parameters}
      After reviewing the literature and aligning the parameters with their real-world significance, 
      we have determined a series of parameters. Due to the large number of parameters, 
      we will only present the table for the main ones:
      \begin{table}[H]
        \centering
        \caption{Parameters}
        \begin{tabular}{cc}
          \toprule
          \rowcolor{customcolor!40} % 设置背景颜色
          Symbols & Description\\
          \midrule
          $123$ & 123\\
          \bottomrule
        \end{tabular}
        \label{tab:Parameters}
      \end{table}
      All of the following models will apply these parameters.
      \subsection{Scenarios Statement}
        Scenarios are stated in Table \ref{tab:Scenarios}, where S represents Scenario, Y for Yes and N for no.
        \begin{table}[H]
          \centering
          \caption{Scenarios}
          \begin{tabular}{lccccccc}
            \toprule
            \rowcolor{customcolor!40} % 设置背景颜色
            conditions & S1 & S2 & S3 & S4 & S5A & S5B & S6 \\
            \midrule
            Agro-Activities & Y & Y & Y & Y & Y & Y & Y \\
            Seasonality & Y & Y & Y & Y & Y & Y & Y \\
            Chemicals & N & Y & Y & N & N & N & N \\
            Reemergence & N & N & Y & Y & Y & Y & Y \\
            Bat & N & N & N & N & Y & N & N \\
            Duck & N & N & N & N & N & Y & N \\
            other methods & N & N & N & N & N & N & Y \\

            \bottomrule
          \end{tabular}
          \label{tab:Scenarios}
        \end{table}
      \subsection{Comparison between S1 and S2: Effects of Chemicals}

      The biomass densities of producers and consumers in S1 and S2 are shown in Figure \ref{fig:S1S2}, respectively.

      \begin{figure}
      \centering
      \includegraphics[width=\linewidth]{images/S1S2.png}
      \caption{Comparison between S1 and S2}
      \label{fig:S1S2}
      \end{figure}

      Analysis reveals that under S1, the ecosystem develops normally; 
      however, rice cannot survive in the long term, and thus, the system cannot evolve into an agricultural ecosystem. 
      This suggests that rice has weak competitive abilities against weeds and poor resistance to pests, 
      making it unable to persist in the ecosystem without human intervention.

      In the early stages of the agricultural ecosystem, before species re-migrate, 
      the model corresponds to S2. At this point, the ecosystem develops normally, 
      rice can survive in the long term, and the system gradually evolves into a mature agricultural ecosystem. 
      This indicates that the traditional chemical-agriculture model is capable of maintaining an agricultural ecosystem.

      \subsection{Scenario 2: Chemicals or Green Agriculture Solutions Used}
        In the discussion of Scenario 2, we consider a realistic situation. 
        A farmer has just cleared a forest to plant rice. 
        Initially, he uses chemicals such as herbicides and pesticides to suppress weeds and pests as the ecosystem gradually develops. 
        When the ecosystem matures to a certain extent, some species that had migrated from the forest ecosystem return, 
        enriching the food web of the farmland ecosystem. After further development, the ecosystem becomes relatively stable, 
        and the farmer stops using herbicides and pesticides, 
        instead turning to a green agriculture solution by introducing ducks and bats into the system.
        Specifically:
        \begin{itemize}
          \item The physiology of ducks prevents them from eating rice, but they can consume weeds and pests.
          \item Ducks are introduced two weeks after each sowing season and are harvested simultaneously with rice at the end of the season.
          \item Bats are introduced all at once and serve as both pollinators and insect predators.
        \end{itemize}
        When the system evolved mature, the final food web of traditional farming mode and green farming mode are shown in 
        Figure \ref{fig:food_web_chem} and Figure \ref{fig:food_web_green} respectively.
        \begin{figure}[H]
          \begin{minipage}[b]{0.45\linewidth}
            \centering
            \includegraphics[height=6cm, keepaspectratio]{images/food_web_chem.pdf}
            \caption{Traditional Mode}
            \label{fig:food_web_chem}
          \end{minipage}
          \hspace{0.05\linewidth}
          \begin{minipage}[b]{0.45\linewidth}
              \centering
              \includegraphics[height=6cm, keepaspectratio]{images/food_web.pdf} % 替换为你的第二张图片路径
              \caption{Green Mode}
              \label{fig:food_web_green}
          \end{minipage}
        \end{figure}
        We will focus on comparing the succession of the ecosystem in the scenarios where humans use chemicals 
        (conventional scenario) and where humans use green agriculture solutions (target scenario). 
        In both cases, the ecosystem is unstable during the initial phase, 
        so we only show the dynamic behavior of the ecosystem after it reaches a stable state.
